Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-06-19 2017-Xudong-SMT/submit-ICTAC2017.tex
Eric: todos from todays skype

\QIN{
And the algorithm published in \cite{henrio:Forte2016} was not the algorithm we are using
so far, which is more precise, defining more details of the algorithm, such as the application of 
the rules on the detection of open transitions and the management of the "data" expressions. 
}

@@

\QIN{[We haven't used the input variables in this paper, we can remove them.]}
\QIN{[To be able to reason about the data flow between pLTSs, we
distinguish \emph{input variables} of the form $?x$ within terms; the function
$\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$, and $iv(t)$ returns its input variables.]}

@@

When building an Open Automaton as the semantics of a pNet, its
\emph{states}, and the shape of the predicates in its
\emph{transitions} have a specific structure:

@@

@@

\subsection{Computing and using open automata}
In this section we present an algorithm to construct the open
automaton representing the behavior of an open pNet, and show
under which conditions this automaton is finite.

@@

@@

\subsection{Combining and Matching using TR2}

@@

We use a brute-force method to generate all the possible open
transitions in the open automaton, using all possible combinations of
synchronization vectors. Naturally this builds some transitions where
the predicates express incompatible constraints. Even if having an
unsatisfiable (symbolic) transition in the open automaton would not be incorrect,
we want to check them for satisfiability, and reduce the number of
transitions and states in the automaton.
In Fig.~\ref{schema:unsat-ot}, we display an example of an
unsatisfiable open transition 
from the result of our example. It shows the case where
the controller C1 wants to move the control from $P$ to $(acc(x);Q)$,
conducting a $\delta$ transition. However, a synchronization
vector is chosen that does not match with this action, and we can
easily find the contradiction in the 
generated predicate term ``$\OTvar{:ra:11:1}=l \!\OTland\! \delta=\OTvar{:ra:11:1}$''.

>>>>

\TODO{[ERIC] rewrite in stronger terms}
\QIN{
And the algorithm published in \cite{henrio:Forte2016} was not the algorithm we are using
so far, which is more precise, defining more details of the algorithm, such as the application of 
the rules on the detection of open transitions and the management of the "data" expressions. 
}

@@

\TODO{[We haven't used the input variables in this paper, we can remove them.]: NO, first see what we use to explain CCS use-case, then leave only a short definition of what we need}
\QIN{[To be able to reason about the data flow between pLTSs, we
distinguish \emph{input variables} of the form $?x$ within terms; the function
$\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$, and $iv(t)$ returns its input variables.]}

@@

\TODO{Relate to the algorithm, or even move to section 5}
When building an Open Automaton as the semantics of a pNet, its
\emph{states}, and the shape of the predicates in its
\emph{transitions} have a specific structure:

@@

\TODO{To be move  by Xudong}

@@

\TODO{To be move / replace by Xudong}
\subsection{Computing and using open automata}
In this section we present an algorithm to construct the open
automaton representing the behavior of an open pNet, and show
under which conditions this automaton is finite.

@@

\TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}

@@

\subsection{Combining and Matching using TR2}
\TODO{Xudong: move here a (new version) of the alogorithm loplevel sketch}

@@

\TODO{ERIC: reduce}
We use a brute-force method to generate all the possible open
transitions in the open automaton, using all possible combinations of
synchronization vectors. Naturally this builds some transitions where
the predicates express incompatible constraints. Even if having an
unsatisfiable (symbolic) transition in the open automaton would not be incorrect,
we want to check them for satisfiability, and reduce the number of
transitions and states in the automaton.
In Fig.~\ref{schema:unsat-ot}, we display an example of an
unsatisfiable open transition 
from the result of our example. It shows the case where
the controller C1 wants to move the control from $P$ to $(acc(x);Q)$,
conducting a $\delta$ transition. However, a synchronization
vector is chosen that does not match with this action, and we can
easily find the contradiction in the 
generated predicate term ``$\OTvar{:ra:11:1}=l \!\OTland\! \delta=\OTvar{:ra:11:1}$''.
